Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-21 def_fidel_echo.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
\begin{equation}
{\rm fidelity} = |\langle \psi_1 |\psi_2  \rangle |^2 
\end{equation}
For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chain (of equal length, hence "bipartite") and $|\psi_2\rangle$ is that of the connected chain with conformal interface. Both of them can be produced by the imaginary time evolution. Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represents the disconnected boundary condition, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$. The logarithmic fidelity is then (twice) the free energy of this diagram
\begin{equation}
\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z
\end{equation}

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{fig_fidelity-DN-lambda-folding.pdf}
\caption{Fidelity of connecting two CFTs. The horizontal axis the imaginary time. Evolution on the two infinitely extended side produces the groundstate of the disconnected and connected chain Hamiltonians. The right diagram is the result of folding the lower part of the diagram up, so that all the boundary are now boundary states.}
\label{fig:fidel}
\end{figure}

The Loschmidt echo is also the (square of the) overlap of two wavefunctions. One of the them the groundstate of the disconnected chain and the other is groundstate evolved by the connected chain Hamiltonian
\begin{equation}
\mathcal{L} = |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2
\end{equation}
The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}. Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt is also the associated the free energy.

\begin{figure}[h]
\centering
\includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
\caption{\color{red} fill in caption of echo diagram}
\label{fig:echo}
\end{figure}

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay patter with respective to these scales in the long wavelength limit. In fact, such kind of computation has been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau 
\end{equation}

The tip of the slit is no longer a twist field with presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing(bcc) operator. These diagrams then becomes the one and two point functions of the bcc operators and the free energy logarithmic term extracts their scaling dimensions.

>>>>

Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
\begin{equation}
{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 
\end{equation}
For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface. Both of them can be produced by the imaginary time evolution. Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represents the disconnected boundary condition, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$. The logarithmic fidelity is then (twice) the free energy of this diagram
\begin{equation}
\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z
\end{equation}

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{fig_fidelity-DN-lambda-folding.pdf}
\caption{Fidelity of connecting two CFTs. The horizontal axis the imaginary time. Evolution of the two infinitely extended sides produces the groundstate of the disconnected and connected chain Hamiltonians. The right diagram is the result of folding the lower part of the diagram up, so that all the boundaries are now boundary states. The solid dot represents boundary changing operator.}
\label{fig:fidel}
\end{figure}

The Loschmidt echo is also the (square of the) overlap of two wavefunctions. One of the them is the groundstate of the disconnected chains and the other is groundstate evolved by the Hamiltonian of the connected chains
\begin{equation}
\mathcal{L} \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2
\end{equation}
The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}. Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy.

\begin{figure}[h]
\centering
\includegraphics[width=1\columnwidth]{fig_echo-DN-lambda-folding.pdf}
\caption{Loschmidt echo of connecting two CFTs. The two infinitely extended sides represent the groundstate of the disconnected chain Hamiltonians. They sandwich the evolution operator at the center, with the Hamiltonian being that of the connected chains. In the folding picture at the right, a,b,c represent the most general boundary conditions of the chains (they all represent `DN' in this case). See the discussion in main text.}
\label{fig:echo}
\end{figure}
\todo[inline]{Tianci: Change the single slit to double slit at the LHS, and add $\tau$ at the RHS?}
If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respective to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau 
\end{equation}

The tip of the slit is no longer a twist field with the presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing(bcc) operator. These diagrams then become the one or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

### 2017-05-21 general_formulation.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

There are however many successful attempts to construct a subset of those bosonic boundary states. One way to do is to impose current operator rather than Virasolo generator constraints, which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989} and can be applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}. Other example utilizes the fusion algebra to generate new boundary states from the known ones\cite{affleck_quantum_2001,bachas_fusion_2008}.

We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002} that begins with a classical boundary condition and then quantize it give the boundary state. The interface obtained is actually the same as using the current algebra constraints\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but we feel that scattering process derived here and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} are more intuitive.

Assume two free Bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the "gluing condition"

\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix}
\end{aligned}\end{equation}
where derivative should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$. As argued, the momentum component of stress tensor is continuous across the interface. As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
\begin{equation}\begin{aligned}
\label{eq:M1M2}
M_1(\theta)=\pm
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda
\end{bmatrix}\quad
M_2(\theta)=\pm
\begin{bmatrix}
0 & \lambda  \\
\lambda^{-1} & 0 
\end{bmatrix}
\end{aligned}\end{equation}
where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.

Several special choice of $\theta$ need to be noted. 
\begin{enumerate}
\item $\theta=0,\pm \frac{\pi}{2}$. In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the fields on either side of the interface cannot transmit to the other side, so the interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions. For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition are imposed on the right and Neumann boundary condition on the left. Hereafter we shall denote this combination as `DN'. Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to ND, DD, NN respectively. 
\item $\theta = \pm \frac{\pi}{4}$. In this case, $M(\theta)$ characterizes a perfectly transmitting interface. For example, there is effectively no interface in the case $M( \frac{\pi}{4})$ which is the traditional periodic boundary condition and we will denote it as P. For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface. 
\end{enumerate}

The physical significance of $\theta$ will be manifest in the scattering process described below. We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and $\partial_{\pm} = \partial_{t} \pm \partial_x $ derivative to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function $t - x$ only and hence represent a right going mode on the right half plane. It is then one of the scattering products that leave the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}\end{equation}

and solve the $S$ matrix for the two cases of $M_1$ and $M_2$

\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix}\quad
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices. The fact of their wavelength independence is an indication of the interface's scale invariance.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{fig_folding_pic.pdf}
\caption{{\color{red} folding picture text}}
\label{fig:folding_pic}
\end{figure}

@@

If we quantize the Boson theory on the interface line $x = 0$, these gluing condition becomes an operator identity for the Boson creation and annihilation of the modes. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free Boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{equation}
\phi(z, \bar{z} ) = \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z}  + \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^n - \bar{a}_{-n } \bar{z}^{-n}   \right)
\end{equation}
where take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ 2\pi ( i\tau - x ) / T } \quad \bar{z} = e^{ -2\pi ( i\tau + x ) / T }
\end{equation}
We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\cos\theta a_n^1-\sin\theta a_n^2 &= +( \cos\theta\bar{a}_{-n}^1-\sin\theta \bar{a}_{-n}^2 ) \\
\sin\theta a_n^1+\cos\theta a_n^2 &= -( \sin\theta\bar{a}_{-n}^1+\cos\theta \bar{a}_{-n}^2 ) 
\end{aligned}
\end{equation}
which is valid on the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous. Eq.~\eqref{eq:bd_state} will be used extensively in the boundary state calculation of fidelity and Loschmidt echo in Sec.~\ref{sec:analytic_numerics}.

\todo[inline]{say sth: connecting to what will follow etc? }

>>>>

There are however many successful attempts to construct a subset of those bosonic boundary states. One way is to impose current operator rather than Virasoro generator constraints, which dates back to the idea of the Ishibashi state\cite{ishibashi_boundary_1989} and can be applied to the multi-component boson with a general compactification lattice\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}. Other examples utilize the fusion algebra to generate new boundary states from the known ones\cite{affleck_quantum_2001,bachas_fusion_2008}.

We here follow the presentation in Ref.~\onlinecite{bachas_permeable_2002} that begins with a classical boundary condition and then quantizes it to give the boundary state. The interface obtained is actually the same as using the current algebra constraints\cite{affleck_quantum_2001,oshikawa_boundary_2010,quella_reflection_2007}, but we feel that scattering process derived here and its relation to the discrete lattice model in Sec.~\ref{sec_sub:free_boson_lattice} are more intuitive.

Assume two free Bosons fields $\phi^1$ and $\phi^2$ live on the left and right half planes respectively. Their interface located at $x = 0$ are characterized by the ``gluing condition"
\begin{equation}\begin{aligned}
\label{eq:def_M}
\begin{pmatrix}
\partial_t\phi^1\\
\partial_x\phi^1
\end{pmatrix}
=M\begin{pmatrix}
\partial_t\phi^2\\
\partial_x\phi^2
\end{pmatrix}
\end{aligned}\end{equation}
where derivative should be understood in the appropriate left and right limits, for example $\partial_x \phi^1$ is evaluated at $ x = 0^-$. As argued, the momentum component of stress tensor is continuous across the interface. As a consequence $M$ is an element of the Lorentz group $O(1,1)$ and can be parameterized as
\begin{equation}\begin{aligned}
\label{eq:M1M2}
M_1(\theta)=\pm
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda
\end{bmatrix}\quad
M_2(\theta)=\pm
\begin{bmatrix}
0 & \lambda  \\
\lambda^{-1} & 0 
\end{bmatrix}
\end{aligned}\end{equation}
where $\lambda=\tan\theta$ for $\theta\in\left[-\frac{\pi}{2},\frac{\pi}{2}\right]$.

Several special choices of $\theta$ need to be noted. 
\begin{enumerate}
\item $\theta=0,\pm \frac{\pi}{2}$. In this case, $\lambda$ (or $\lambda^{-1}$) appears to be singular and the field on either side of the interface cannot transmit to the other. The interface reduces to individual boundary conditions for the boson on the left and right half planes: they are combination of Dirichlet and Neumann boundary conditions. For example, $\lambda = 0$ for $M_1$ implies $\partial_x\phi^1 = \partial_t\phi^2 =0$, which means that Dirichlet boundary condition is imposed on the right and Neumann boundary condition on the left. Hereafter we shall denote this combination as `DN'. Similarly $M_1(\pm\frac{\pi}{2}),M_2(0),M_2(\pm \frac{\pi}{2})$ correspond to `ND', `DD', `NN' respectively. 
\item $\theta = \pm \frac{\pi}{4}$. In this case, $M_1(\theta)$ characterizes a perfectly transmitting interface. For example, there is effectively no interface in the case $M_1( \frac{\pi}{4})$ which is the traditional periodic boundary condition and we will denote it as P. For the other three cases, despite picking up a phase, the two counter propagating modes are still fully transmitted cross the interface. 
\end{enumerate}

The physical significance of $\theta$ will be manifest in the scattering process described below. We rewrite the Eq.~\eqref{eq:def_M} in the coordinates $t\pm x$ and $\partial_{\pm} = \partial_{t} \pm \partial_x $ to extract the left and right going modes. For example, $\partial_{-} \phi^2$ will be a function $t - x$ and hence represents a right going mode on the right half plane. It is then one of the scattering products that leaves the interface. On the other hand $\partial_{-} \phi^1$ and $\partial_{+} \phi^2$ are modes that approaching the interface from their respective domain. We therefore establish the scattering relation 
\begin{equation}\begin{aligned}
\label{eq:def_S}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}\end{equation}
and solve the $S$ matrix for the two cases of $M_1$ and $M_2$
\begin{equation}\begin{aligned}
\label{eq:S1_S2}
S_1(\theta)=\begin{bmatrix}
\cos 2\theta & \sin 2\theta \\
\sin 2\theta & -\cos 2\theta
\end{bmatrix}\quad
S_2(\theta)=\begin{bmatrix}
-\cos 2\theta & \sin 2\theta \\
-\sin 2\theta & -\cos 2\theta
\end{bmatrix}
\end{aligned}\end{equation}
For generic values of $\theta$, the interface is partially-transmitting, whose transmission and reflection coefficients can be read off from the scattering matrices. The fact of their wavelength independence is an indication of scale invariance of the interface.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{fig_folding_pic.pdf}
\caption{Folding picture for penetrable interface. Left panel: World line of the penetrable interface. $\partial_\pm\phi^{1,2}$ denote the left and right going modes in their respective domain. Right panel: Folding operation that sends $\phi^2(x)$ to $\phi^2(-x)$. The dashline represents the \emph{im}penetrable boundary for the resulting tensor theory.}
\label{fig:folding_pic}
\end{figure}

@@

If we quantize the Boson theory on the interface line $x = 0$, these gluing conditions become an operator identity for the boson creation and annihilation of the modes. We shall interpret these identities to be valid only when acting on the boundary states. The mode expansion of free boson on $x = 0$\cite{di_francesco_conformal_1997} is
\begin{equation}
\phi(z, \bar{z} ) = \phi_0 - \frac{i}{4\pi g } \pi_0 \ln z \bar{z}  + \frac{i}{\sqrt{4\pi g} } \sum_{n \ne 0 } \frac{1}{n} \left(a_n z^n - \bar{a}_{-n } \bar{z}^{-n}   \right)
\end{equation}
where take $T$ to be time period and the following choice of the holomorphic and anti-holomorphic coordinates
\begin{equation}
z= e^{ 2\pi ( i\tau - x ) / T } \quad \bar{z} = e^{ -2\pi ( i\tau + x ) / T }
\end{equation}
We end up with a set of operator identities for each mode
\begin{equation}
\begin{aligned}
\label{eq:rotation_a_basis}
\cos\theta a_n^1-\sin\theta a_n^2 &= +( \cos\theta\bar{a}_{-n}^1-\sin\theta \bar{a}_{-n}^2 ) \\
\sin\theta a_n^1+\cos\theta a_n^2 &= -( \sin\theta\bar{a}_{-n}^1+\cos\theta \bar{a}_{-n}^2 ) 
\end{aligned}
\end{equation}
which is valid on the following boundary state
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle 
& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
\begin{pmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{pmatrix}
S_1( \theta )
\begin{pmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{pmatrix} \Big\} |0\rangle
\end{aligned}
\end{equation}
where $S_1(\theta) $ is precisely the scattering matrix in Eq.~\eqref{eq:def_S}. The calculation for the case $M=M_2(\theta)$ is completely analogous. Eq.~\eqref{eq:bd_state} will be used extensively in the boundary state calculation of fidelity and Loschmidt echo in Sec.~\ref{sec:analytic_numerics}.

### 2017-05-21 intro.tex
[draft] Some captions added, prove read most of the parts to correct typo and adjust the format. Forgot to write abstract, and structure of the paper. Will do it tomorrow

% quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
In (one-dimensional) quantum critical systems, the presence of physical boundary and isolated impurity weakly break the conformal symmetry. Simply put, they scatter and hence relate the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}. Operators close to the boundary are interpreted as boundary condition changing operator\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT). Their correlation functions exhibit different critical exponent from the bulk\cite{cardy_conformal_1984}. One example is the "Anderson orthogonality catastrophe", where the core hole creates a potential that act as an impurity to the conduction band. The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency. There are numerous impurity problem of this kind that has been studied in the last few decades, such as magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity. The "cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) cross the system. As shown in Fig.~\ref{fig:cut-and-join}, one first prepares the ground states of the critical chain A and B, and then connect them at $t = 0$ and evolve. Various quantities are used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems. And the authors ascribe the growth to the proliferation and propagation of quasi-particle excitation emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} take A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution. In this mode, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with the boundary critical exponent.

\begin{figure}[htb]
\centering
\includegraphics[width=\textwidth]{fig_cut_and_join.pdf}
\caption{Cut-and-join quench protocol. Left panel: prepare the ground states of two separated chains and joined them at $t = 0$, then do the time evolution with whole chain Hamiltonian. Right panel: spacetime diagram of the cut and join protocol. The solid line represents the boundaries of the two disconnected chains. It is totally reflective for the incident particles on both sides. The dashed line is the world line of the junction, which we will call interface. It could either be totally transparent or partially permeable, depending the types of theories of A and B.}
\label{fig:cut-and-join}
\end{figure}

% All of these are the same CFTs. we consider different CFTs, the mediating particle or primary field will be different, from the S matrix point of view.
In the path integral language, the "cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}. The separating ground stats prepared before $t = 0$ are joined to form a new type of interface between them. Before the quench, the slit before $t = 0$ represents the boundary that are completely reflective to the injecting particles. The joining turns on the transmission from one side to the other. In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of \onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.

It would therefore be interesting to consider to connect two different CFTs in the "cut-and-join" protocol. The interface produced will interpolate between the total reflective and complete transparent ones. It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}. There is also non-compact free boson/free fermion lattice realization, which was used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study entanglement properties. In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the compact Boson case, it is controlled by the ratio of the compactification radii and in the free lattice Boson case by ratio of masses. We expect it to be tunable in the a realistic experimental setting.

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
Fidelity and Loschmidt echo are the two quantities we compute to extract information from the quench process. Fidelity is the (square of) the overlap of the ground state wavefunction of the Hamiltonian before and after the quench. There is no dynamic information in fidelity, nevertheless its finite size effect also reveal the boundary critical exponent that maybe be diagnostic in Loschmidt echo computation. The Loschmidt echo is (square of) the overlap of the wavefunction before the quench and the one evolved at time $t$. The Loschmidt echo decays with a power law for the lack of length scale in the $t \rightarrow \infty$ limit. Its exponent has been calculated for various geometries and combinations of normal boundary conditions of the same CFT in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. What we do in this paper is to extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.

>>>>

% quantum impurity problem,  boundary critical phenomena, Anderson orthogonality catastrophe
In (one-dimensional) quantum critical systems, the presence of physical boundary and isolated impurity weakly break the conformal symmetry. Simply put, they scatter and hence relate the otherwise independent modes and therefore demonstrate novel boundary critical phenomena\cite{cardy_boundary_2004}. Operators close to the boundary are interpreted as boundary condition changing operators\cite{oshikawa_boundary_1997,affleck_boundary_1997} in the boundary conformal field theory (CFT). Their correlation functions exhibit different critical exponent from the bulk\cite{cardy_conformal_1984}. One example is the ``Anderson orthogonality catastrophe", where the core hole creates a potential that acts as an impurity to the conduction band. The X-ray absorption rate will then have a power singularity of boundary exponent\cite{affleck_boundary_1997} at the resonance frequency. There are numerous impurity problems of this kind that have been studied in the last few decades, such as magnetic impurity in spin chain\cite{eggert_magnetic_1992}, boundary and impurity effects in Luttinger liquid\cite{fabrizio_interacting_1995}, entanglement of the defects\cite{peschel_entanglement_2005, igloi_entanglement_2009,calabrese_entanglement_2012} \etc

% non-equilibrium dynamics, particle mediate the two parts, Cardy cut-and-join protocol, Vassur majarana
Recently, more attention has been paid to the non-equilibrium dynamics of the quantum impurity. The ``cut-and-join" quench protocol is a popular framework to study the spreading of influence from the localized impurity (or boundary) cross the system. As shown in Fig.~\ref{fig:cut-and-join}, one first prepares the ground states of the critical chain A and B, and then connects them at $t = 0$ and evolves. Various quantities are used to detect the information in the quench process. For instance, Ref.~\onlinecite{calabrese_entanglement_2007, calabrese_quantum_2016} find a logarithmic increase of entanglement entropy in subsystem $A$, when both $A$ and $B$ are identical critical systems. And the authors ascribe the growth to the proliferation and propagation of quasi-particle excitations emitted at the joint. Ref.~\onlinecite{vasseur_universal_2014} takes A to be a normal lead and B to be a topological superconductor in topological phase and calculate the Loschmidt echo (overlap of wavefunction, see below) of the evolution. In this model, effectively it is the Majorana zero mode which mediates the left and right modes of the free fermion that are responsible for the universal power law decay of the Loschmidt echo with the boundary critical exponent.

\begin{figure}[h]
\includegraphics[width=1\columnwidth]{fig_cut_and_join.pdf}
\caption{Cut-and-join quench protocol. Left panel: prepare the ground states of two separated chains and joine them at $t = 0$, then do the time evolution with whole chain Hamiltonian. Right panel: spacetime diagram of the cut and join protocol. The solid line represents the boundaries of the two disconnected chains. It is totally reflective for the incident particles on both sides. The dashed line is the world line of the junction, which we will call interface. It could either be totally transparent or partially permeable, depending the types of theories of A and B.}
\label{fig:cut-and-join}
\end{figure}

% All of these are the same CFTs. we consider different CFTs, the mediating particle or primary field will be different, from the S matrix point of view.
In the path integral language, the ``cut-and-join" protocol corresponds to a spacetime diagram as shown in Fig.~\ref{fig:cut-and-join}. The separating ground stats prepared before $t = 0$ are joined to form a new type of interface between them. Before the quench, the slit represents boundaries that are completely reflective to the injecting particles. The joining turns on the transmission from one side to the other. In the entanglement entropy and Loschmidt echo examples cited above\cite{calabrese_entanglement_2007, calabrese_quantum_2016, vasseur_universal_2014}, the two sides of the CFTs are the same (chiral fermion CFT in the case of Ref.~\onlinecite{vasseur_universal_2014}) and the boundary becomes totally transparent after the joining.

It would therefore be interesting to connect two different CFTs in the ``cut-and-join" protocol. The interface produced will interpolate between the total reflective and complete transparent ones. It can be realized as interface of two free compact Boson theories with different compactification radii\cite{bachas_permeable_2002}. There are also non-compact free boson/free fermion lattice realizations, which were used to numerically and analytically\cite{peschel_exact_2012,sakai_entanglement_2008} study entanglement properties. In these models, there is a parameter $\lambda$ that is directly related to the transmission coefficient. In the compact Boson case, it is controlled by the ratio of the compactification radii and in the free lattice Boson case by ratio of masses. We expect it to be tunable in a realistic experimental setting.

% fidelity and Loschmidt echo are quantities that extract boundary critical exponents, may reveal the nature of the mediating particle 
Fidelity and Loschmidt echo are the two quantities we compute to extract information from the quench process. Fidelity is the (square of) the overlap of the ground state wavefunction of the Hamiltonian before and after the quench. There is no dynamic information in fidelity, nevertheless its finite size effect also reveals the boundary critical exponent that may be diagnostic in Loschmidt echo computation. The Loschmidt echo is (square of) the overlap of the wavefunction before the quench and the one evolved at time $t$. The Loschmidt echo decays with a power law for the lack of length scale in the $t \rightarrow \infty$ limit. Its exponent has been calculated for various geometries and combinations of normal boundary conditions of the same CFT in \onlinecite{stephan_logarithmic_2013,stephan_local_2011}. What we do in this paper is to extend the analysis to the aforementioned parametric interface of (possibly) different CFTs.
